R for Clinical Study Reports and Submission

### 2023-06-04 project-folder.qmd
RStudio -> Posit except RStudio IDE

We will use the [`esubdemo`](https://github.com/elong0527/esubdemo) R package to
illustrate the project folder structure for the A&R project. You can
[clone](https://happygitwithr.com/rstudio-git-github.html#clone-the-new-github-repository-to-your-computer-via-rstudio)
the project using RStudio with

@@

First, we introduce the control of the R version.
In the esubdemo project, a reproducible environment is created when you open
the `esubdemo.Rproj` from RStudio.
When we open the `esubdemo` project, RStudio will execute the R code in `.Rprofile` automatically.
So we can use `.Rprofile` to set up a reproducible environment.
More details can be found in <https://rstats.wtf/r-startup.html>.
After we open the `esubdemo` project, the code in `.Rprofile` will
automatically check the current R version is the same as we defined in `.Rprofile`.

@@

::: {.callout-tip}
A cloud-based R environment (e.g., RStudio Workbench)
can enhance the reproducibility within an organization
by using the same operating system, R version, and R package versions for an A&R project.
More details can be found at <https://environments.rstudio.com/>.
:::

>>>>

We will use the [`esubdemo`](https://github.com/elong0527/esubdemo) R package to
illustrate the project folder structure for the A&R project. You can
[clone](https://happygitwithr.com/rstudio-git-github.html#clone-the-new-github-repository-to-your-computer-via-rstudio)
the project using RStudio IDE with

@@

First, we introduce the control of the R version.
In the esubdemo project, a reproducible environment is created when you open
the `esubdemo.Rproj` from RStudio IDE.
When we open the `esubdemo` project, RStudio IDE will execute the R code in `.Rprofile` automatically.
So we can use `.Rprofile` to set up a reproducible environment.
More details can be found in <https://rstats.wtf/r-startup.html>.
After we open the `esubdemo` project, the code in `.Rprofile` will
automatically check the current R version is the same as we defined in `.Rprofile`.

@@

::: {.callout-tip}
A cloud-based R environment (e.g., [Posit Workbench](https://posit.co/products/enterprise/workbench/))
can enhance the reproducibility within an organization
by using the same operating system, R version, and R package versions for an A&R project.
More details can be found at <https://environments.rstudio.com/>.
:::

### 2023-06-04 slides/fda-workshop-slides.Rmd
fix brocken link
fix broken link
RStudio -> Posit except RStudio IDE

- During the workshop, we will use `esubdemo` project.
  - `esubdemo` is shared in RStudio Cloud (<https://rstudio.cloud/>)
  - You can also clone the `esubdemo` project to your local RStudio.

@@

<https://r4csr.org/disposition.html>

@@

<https://r4csr.org/efficacy-table.html>

@@

<https://r4csr.org/specific-ae.html>

@@

<https://r4csr.org/assemble.html>

@@

<https://r4csr.org/folder.html>

>>>>

- During the workshop, we will use `esubdemo` project.
  - `esubdemo` is shared in Posit Cloud (<https://posit.cloud/>)
  - You can also clone the `esubdemo` project to your local RStudio IDE.

@@

<https://r4csr.org/tlf-disposition.html>

@@

<https://r4csr.org/tlf-efficacy-ancova.html>

@@

<https://r4csr.org/tlf-ae-specific.html>

@@

<https://r4csr.org/tlf-assemble.html>

@@

<https://r4csr.org/project-folder.html>

### 2023-06-04 slides/r4csr-gwu.Rmd
Built site for gh-pages
RStudio -> Posit except RStudio IDE

- Fixed R version: e.g., R 4.1.0
- Fixed R package snapshot date: e.g., 2021-08-31
  - [RStudio Public Package Manager](https://packagemanager.rstudio.com/)
  - [CRAN Time Machine by MRAN](https://mran.microsoft.com/timemachine)
- Flexibility of input and output path:
  - Define path as parameter.
- eCTD deliverables dry-run in Windows environment
- Provide steps to follow in [ADRG appendix](https://github.com/RConsortium/submissions-pilot1-to-fda/blob/main/m5/datasets/rconsortiumpilot1/analysis/adam/datasets/adrg.pdf)

@@

More details: <https://r4csr.org/folder.html>

>>>>

- Fixed R version: e.g., R 4.1.0
- Fixed R package snapshot date: e.g., 2021-08-31
  - [Posit Package Manager](https://packagemanager.posit.co/)
  - [CRAN Time Machine by MRAN](https://mran.microsoft.com/timemachine)
- Flexibility of input and output path:
  - Define path as parameter.
- eCTD deliverables dry-run in Windows environment
- Provide steps to follow in [ADRG appendix](https://github.com/RConsortium/submissions-pilot1-to-fda/blob/main/m5/datasets/rconsortiumpilot1/analysis/adam/datasets/adrg.pdf)

@@

More details: <https://r4csr.org/project-folder.html>
